Gap Puzzles

### 2020-01-04 gap/article/llncs2e/article.tex
Added article first part

\begin{document}
%
\title{Gap}

@@

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

\section{Introduction}

\section{Problem Description}

@@

\subsection{Evaluation Function}

@@

\section{Solution Presentation}

@@

\begin{thebibliography}{8}
    \bibitem{ref_article1}
    Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

    \bibitem{ref_url1}
    LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
    Oct 2017
    \end{thebibliography}

>>>>

\begin{document}
%
\title{Gap Puzzles}

@@

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
This project was developed during the the Logical Programing Course in the context of the year
of the Integrated Masters in in Informatics and Computing Engineering at The Faculty of Engineering
of the University of Porto. The goal was to solve a problem using the Prolog programming language,
more specifically, using Constraint Logic Programming over Finite Domains (clpfd) library, that's defined
in the SICStus Prolog distribution. 
In the specific case of our team, the problem in question is the Gap Puzzle, which is defined in detail in
\textbf{Section 2}.
In order to solve the problem, Prolog constraint programming was used. This type of programming grants us the
advantage of fast computation, requiring a somewhat simple and little verbosed kind of programming. Using constraints,
we can simply define all the constraints of our problem (in the case of puzzles these are the rules of the puzzle), 
which in the case of more complex problems is not trivial. Then, after defining the solution search algorithm, 
the clpfd library will search for solutions.
\textbf{CONCLUSÕES}

\keywords{Prolog  \and Constraint Programing \and Gap Puzzle.}
\end{abstract}

\pagebreak

\section{Introduction}
\paragraph{}
This goal of the project was to elaborate a Prolog program that, given a board order, computes all the solutions of the 
Gap Puzzle for that board order. 
Optimization is a relevant factor here. Different ways of defining constraints can lead us to the same set of 
solutions, but computation times can vary greatly. So, one of the concerns during the development of this project 
was to find solutions as fast as possible.

\paragraph{}
Bellow we shortly explain the following sections of this article.

\begin{itemize}
    \item \textbf{Problem Description:} Detailed description of the problem we are solving and the rules of Gap Puzzles

    \item \textbf{Approach:} 
    \begin{itemize}
        \item \textbf{Decision Variables:} 
        \item \textbf{Constraints:}
        \item \textbf{Search Strategy:} 
    \end{itemize}

    \item \textbf{Solution Presentation:} Description of how solutions are presented in an intelligible way.
    \item \textbf{Results:}
    \item \textbf{Conclusions:}
\end{itemize}

\section{Problem Description}
The problem in question is the solution is the solution of the Gap Puzzle. Gap is a very simple puzzle, yet a challenging
one. We have grid of arbitrary size and our goal, is to shade two squares of the grid in every row and column, such that 
two shaded squares do not touch, even at the corners. Because there is more than one solution for every grid order,
in the puzzle form of the problem, there are numbers on the side of the grid to indicate the number of non shaded squares
there must exist between two shaded squares in that row or column. The figure below illustrates an example of puzzle with
order 5.

\begin{figure}
\includegraphics[width=\textwidth]{images/figure1.png}
\caption{Gap Puzzle example} \label{fig1}
\end{figure}

\paragraph{}
Although they are very interesting, these specific puzzles do not interest us. We are interested in finding arbitrary 
solutions for a problem with a given order.

@@

@@

\section{Solution Presentation}
\paragraph{}
For solution presentation there the \textbf{display\_gap(+Sol,+Len)} was elaborated. This predicate receives the \textit{Sol}
list, which is a prolog list containing the coordinates of all grid cells to be shaded for that solution, and \textit{Len},
which is the length of a row, that is, the order of the board the solution given applies to. In order to do this, this 
predicate uses the three predicates explained bellow.

\paragraph{}
This predicate uses the \textbf{empty\_board(-B,+Len)} which creates a list of lists representing an empty grid, with order \textit{Len},
this new grid is then unified with \textit{B}. This predicate works by appending new atoms, representing an empty cell (\textbf{' '}, 
a single space character) to an empty starting list. Once this list has the desired length, this list is then replicated 
several times to form a new empty grid.

\paragraph{}
Then, we use the \textbf{process\_board(+Board,+Sol,-NewBoard)} to substitute all the empty cells in the positions given
by solution list, with the \textbf{'X'} atom. This represents a shaded cell. In order to make the substitution we defined
the \textbf{replaceN(+List,+N,+NewElem,Res)} predicate. This predicate substitutes the element of order \textit{N} in 
\textit{List} to the element \textit{NewElem}, then unifies the resulting list with \textit{NewBoard}.

\paragraph{}
Finally, the predicate \textbf{display\_board(+Board)} was defined to display the board \textit{Board}. This predicate
writes the separators in the screen and then displays each row of the grid, using the right format. Bellow, we can see a
displayed board.

\begin{figure}
    \begin{center}
        \includegraphics[scale=0.5]{images/fig2.png}
        \caption{Solution Display Example} \label{fig2}
    \end{center}
\end{figure}

@@

\begin{thebibliography}{8}
    \bibitem{ref_url}
    Erich Friedman's Puzzle Palace - Gap Puzzles, Copyright Erich Friedman, 2010. 
    \url{https://www2.stetson.edu/~efriedma/puzzle/gap/}. 
    Last accessed 4 Jan 2020
    \end{thebibliography}
